\documentclass[12pt]{article}
\usepackage{array,ragged2e}
\usepackage[svgnames,table]{xcolor}
\definecolor{grey}{HTML}{3E3D3C}
%\color{gray}
\usepackage{longtable}
\usepackage{changepage}
\usepackage{setspace}
\usepackage{hhline}
%\usepackage{multicol}
\usepackage{lastpage}
\usepackage{multirow}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}
\usepackage[paperheight=11.0in,paperwidth=8.5in,top=1in,left=1in,right=1in,bottom=1in]{geometry}
\usepackage[none]{hyphenat}
\usepackage{fontspec}
\usepackage{microtype}
\setmainfont[AutoFakeSlant=0.3]{Rasa}

\hypersetup{colorlinks,allcolors=[HTML]{0B5394},pdfinfo={Title={Curriculum Vitae of Bryan Dosono},Author={Bryan Dosono},Creator={Bryan Dosono},Subject={Curriculum Vitae},Keywords={Curriculum Vitae},CreationDate={D:20260608080808}}}
%\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{R}[1]{>{\RaggedLeft\arraybackslash}p{#1}}
\newcolumntype{L}[1]{>{\RaggedRight\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\Centering\arraybackslash}p{#1}}
\pagestyle{fancy}
\fancyhf{}

\cfoot{
\textcolor{gray}{
\begin{tabular}{R{0.75in}p{5in}}
{\footnotesize Page \thepage/22} & {\footnotesize Dosono, CV}\\
\end{tabular}}}

\renewcommand{\headrulewidth}{0pt}
\setlength{\topsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}
\renewcommand{\arraystretch}{1}
%\renewcommand{\baselinestretch}{1.1}
%\setlength\tabcolsep{0pt}

\usepackage[normalem]{ulem}

\begin{document} 
\RaggedRight{\color{grey}
\setlength \extrarowheight{6pt}

\begin{longtable}{R{0.75in}p{5.0in}}
%\begin{longtable}{R{0.75in}p{5.0in}p{0.75in}}

& {\Huge \textcolor{black}{\MakeUppercase{Bryan Dosono, Ph.D.}} } \\
& {\normalsize \href{mailto:info@bdosono.com}{info@bdosono.com} • \href{https://www.bdosono.com}{www.bdosono.com} \break
Curriculum Vitae, July 2026} \\ \\

\sout{\hfill} 
& \par \Large \textcolor{black}{\uppercase{Appointments\hspace{6pt} \sout{\hfill}}} \medskip \\

& \large \textcolor{black}{\uppercase{Industry Experience}}\\ 

\footnotesize{\vfill 2025 \hfill} & \href{https://www.disney.com/}{The Walt Disney Company} \break Principal Researcher, Disney Entertainment and ESPN Product Technology \\

\footnotesize{\vfill 2025 \hfill} & 
\href{https://www.okx.com/}{OKX, Inc.} \break Principal, CEO Office\\

\footnotesize{\vfill 2023 -- 25 \vspace{1mm} \break 2022 -- 23 \vspace{1mm} \break 2020 -- 21 \hfill} & \href{https://ebay.com/}{eBay, Inc.} \break Lead User Experience Researcher, Regulatory and Financial Services \break Senior User Experience Researcher, Identity and Security \break Design Researcher, Payments and Protections\\

\footnotesize{\vfill 2019 -- 20 \vspace{1mm} \break 2018 \hfill} & \href{https://airbnb.com/}{Airbnb, Inc.} \break Experience Researcher, Trust Growth: Business Enablement \break Experience Research Intern, Trust Defense: Account Integrity\\

\footnotesize{\vfill 2018 -- 19 \hfill} & \href{https://www.nasa.gov/}{National Aeronautics and Space Administration} \break Virtual Student Federal Service Intern, Office of the Chief Technologist\\

\footnotesize{\vfill 2013 \vspace{1mm} \break 2012 -- 13 \hfill} & \href{https://www.google.com/policyfellowship/2013fellows.html}{Google, Inc.} \break Policy Fellow, New America Foundation, Open Technology Institute \break Student Ambassador, Google for Education\\

\footnotesize{\vfill 2008} & \href{https://www.engr.washington.edu/current/studentprogs/alva}{The Boeing Company} \break Engineering Intern, Interiors Integration \medskip \\ 

& \large \textcolor{black}{\uppercase{Academic Experience}}\\

\footnotesize{\vfill 2013 -- 19 \vspace{1mm} \break 2014 -- 17 \hfill} & \href{https://ischool.syr.edu/research/human-centered-computing-and-design-lab/}{Syracuse University}\break Doctoral Researcher, Human-Centered Computing and Design Lab\break Doctoral Researcher, Social Computing Systems Lab\\

\footnotesize{\vfill 2018 -- 17 \vspace{1mm} \break 2016 \hfill} & \href{https://www.sis.pitt.edu/i3/phd-fellows/fellow-profiles.html}{iSchool Inclusion Institute} \break Research Advisor, Summer Research Experience for Undergraduates \break Teaching Fellow, Python Programming Intensive\\

\footnotesize{\vfill 2012 -- 13 \hfill} & \href{https://faculty.washington.edu/ajko/lab}{University of Washington} \break Undergraduate Researcher, Code and Cognition Lab \medskip \\ \pagebreak

& \large \textcolor{black}{\uppercase{Nonprofit Experience}}\\

\footnotesize{\vspace{0mm} \break 2026 \vspace{1mm} \break 2024 -- 25 \vspace{1mm} \break 2020 -- 23 \vspace{1mm} \break 2017 -- 19 \vspace{1mm} \break 2016 \hfill} & \href{https://www.napahq.org/}{National Asian Pacific Islander Desi American Panhellenic Association} \break Immediate Past Chair \break Executive Chair \break Director of Research and Development \break Director of Membership and Standards \break Director of Technology\\

\footnotesize{\vspace{0mm} \break 2023 -- 26\vspace{1mm} \break 2020 -- 22\vspace{1mm} \break 2018 -- 20 \vspace{1mm} \break 2016 -- 18 \vspace{1mm} \break 2013 -- 16 \hfill} & \href{https://lambdaphiepsilon.org/message-from-president-20/}{Lambda Phi Epsilon International Fraternity, Inc.} \break Trustee, Scholarship Foundation \break President and Chief Executive Officer, Board of Directors \break External Vice President, Board of Directors \break Director of Communications, International Board \break Public Relations Officer, International Board  \medskip\\\\

\sout{\hfill} 
& \par \Large \textcolor{black}{\uppercase{Education\hspace{6pt} \sout{\hfill}}} \medskip \\

& \large \textcolor{black}{\uppercase{Executive Certificate}}\\
\footnotesize{2024} & \href{https://www.hks.harvard.edu/}{Public Policy} (In Progress)
\break Harvard University, John F. Kennedy School of Government \break Program: Behavioral Insights and Public Policy\medskip \\ 

& \large \textcolor{black}{\uppercase{Doctor of Philosophy}}\\
\footnotesize{2019} & \href{https://web.archive.org/web/20200311064951/https://ischool.syr.edu/people/directories/view/bdosono/}{Information Science and Technology}
\break Syracuse University (SU), School of Information Studies \break Concentration: Data Science \medskip \\ 

& \large \textcolor{black}{\uppercase{Bachelor of Science}}\\
\footnotesize{2013} & \href{https://web.archive.org/web/20170203233921/http://ischool.uw.edu/research/student-research/dosono}{{Informatics: Human-Computer Interaction}} \break University of Washington (UW), Information School \break College Honors, Phi Beta Kappa, Magna Cum Laude, Minor: Music\\\\

\sout{\hfill} 
& \par \Large \textcolor{black}{\uppercase{Publications\hspace{6pt} \sout{\hfill}}} \medskip \\

& \large \textcolor{black}{\uppercase{Dissertation}}\\

\footnotesize{[D1]} & \href{https://surface.syr.edu/etd/1034/}{Dosono, B.} (2019). Identity work of Asian Americans and Pacific Islanders on Reddit: Traversals of deliberation, moderation, and decolonization. Doctoral dissertation, Syracuse University. \medskip \\ \pagebreak

& \large \textcolor{black}{\uppercase{Peer-reviewed Journal Publications}}\\

\footnotesize{[J8]} & Heath, C. R., \href{https://doi.org/10.1007/s12325-026-03634-z}{Dosono, B.}, Shi, V. Y., Soung, J., Smith Begolka, W., Bacci, E. D., Constantine, M. L., Correll, J. R., Mitchell, B., Atwater, A. R., Pierce, E. J.,  Chovatiya, R. (2026). Variations in healthcare provider interactions and treatment satisfaction by patient race and ethnicity: A survey of adults with Atopic Dermatitis. \textit{Advances in Therapy}, 1-20.\\

\footnotesize{[J7]} & Becker, S. L., Bash, G. N., Smith Begolka, W., Wallace-Hood, T., Takeshita, J., Drucker, A. M., Silverberg, J. I., Eichenfield, L. F., Abuabara, K., \href{https://doi.org/10.1016/j.jid.2025.07.025}{Dosono, B.}, Hamilton, A., Okereke, R., Simpson, E. L. (2025). Improving the quality of atopic dermatitis epidemiological research in the United States- A systematic review of disease definitions and related content in national surveys. \textit{Journal of Investigative Dermatology}.\\

\footnotesize{[J6]} & Tran, S., Lin, C., \href{https://doi.org/10.1177/20563051251363215}{Dosono, B.}, Cotter, K. (2025). TikTok as a tool for identity work among the Hoa ethnic community. \textit{Social Media + Society}, 11(3).\\

\footnotesize{[J5]} & Lyu, Y., Cai, J., \href{https://dl.acm.org/doi/10.1145/3687013}{Dosono, B.}, Yadav, D., Carroll, J. M. (2024). ``I upload... all types of different things to say the world of blindness is more than what they think it is'': A study of Blind TikTokers' identity work from a flourishing perspective. \textit{Proceedings of the ACM on Human-Computer Interaction}. 8(CSCW2). 1-24. \textbf{Honorable Mention Award}.\\

\footnotesize{[J4]} & \href{https://dl.acm.org/doi/10.1145/3392881?cid=88158835957}{Dosono, B.}, Semaan, B. (2020). Decolonizing tactics as collective resilience: Identity work of AAPI communities on Reddit. \textit{Proceedings of the ACM on Human-Computer Interaction}. 4(CSCW1), 1-20. \textbf{Best Paper Award}.\\

\footnotesize{[J3]} & \href{https://doi.org/10.1109/MIC.2018.112101619}{Dosono, B.}, Hayes, J., Wang, Y. (2018). Toward accessible authentication: Learning from people with visual impairments. \textit{IEEE Internet Computing}, 22(2). 62-70.\\

\footnotesize{[J2]} & \href{https://dl.acm.org/authorize?N42807}{Dosono, B.}, Rashidi, Y., Akter, T., Semaan, B., Kapadia, A. (2017). Challenges in transitioning from civil to military culture: Hyper-selective disclosure through ICTs. \textit{Proceedings of the ACM on Human-Computer Interaction}, 1. 41:1-23 ACM.\\

\footnotesize{[J1]} & Gomez, R., Pather, S., \href{https://doi.org/10.1002/j.1681-4835.2012.tb00366.x}{Dosono, B.} (2012). Public access computing in South Africa: Old lessons and new challenges. \textit{The Electronic Journal of Information Systems in Developing Countries}, 52(1). 1-16. \medskip \\

& \large \textcolor{black}{\uppercase{Peer-reviewed Conference Proceedings}}\\

\footnotesize{[C15]} & Akter, T., \href{https://www.usenix.org/conference/usenixsecurity20/presentation/akter}{Dosono, B.}, Ahmed, T., Kapadia, A., Semaan, B. (2019). ``I am uncomfortable sharing what I can't see'': Privacy concerns of the visually impaired with camera based assistive applications. \textit{29th {USENIX} Security Symposium}.\\

\footnotesize{[C14]} & \href{https://dl.acm.org/authorize?N680367}{Dosono, B.}, Semaan, B. (2019). Moderation practices as emotional labor in sustaining online communities: The case of AAPI identity work on Reddit. \textit{Proceedings of the 2019 CHI Conference on Human Factors in Computing Systems}. 142:1-142:13. ACM.\\

\footnotesize{[C13]} & Grimaldi, V., Figueroa, J., Sullivan, J., \href{https://doi.org/10.1007/978-3-030-15742-5_29}{Dosono, B.} (2019). From gridiron gang to game plan: Impact of ICTs on student athlete information seeking practices, routines, and long-term goals. \textit{Information in Contemporary Society}. 290-301. Springer International Publishing.\\

\footnotesize{[C12]} & \href{https://dl.acm.org/authorize?N658208}{Dosono, B.}, Semaan, B. (2018). Identity work as deliberation: AAPI political discourse in the 2016 US Presidential Election. \textit{Proceedings of the 2018 CHI Conference on Human Factors in Computing Systems}. 633:1-12. ACM.\\

\footnotesize{[C11]} & Booth, K., \href{https://doi.org/10.1007/978-3-319-78105-1_75}{Dosono, B.}, Redmiles, E., Morales, M., Depew, M., Herman, E., Trahan, K., Tananis, C., Farzan, R. (2018). Diversifying the next generation of information scientists: Six years of implementation and outcomes for a year-long REU program. \textit{Transforming Digital Worlds}. 655-664. Springer International Publishing.\\

\footnotesize{[C10]} & \href{https://dl.acm.org/authorize?N41342}{Dosono, B.}, Semaan, B., Hemsley, J. (2017). Exploring AAPI identity online: Political ideology as a factor affecting identity work on Reddit. \textit{Proceedings of the 2017 CHI Conference Extended Abstracts on Human Factors in Computing Systems}. 2528-2535. ACM.\\

\footnotesize{[C9]} & Bratt, S., Semaan, B., Britton, L., \href{https://web.archive.org/web/20250618175300/https://idl.iscram.org/files/sarahbratt/2017/2017_SarahBratt_etal2017.pdf}{Dosono, B.}, Franco, Z. (2017). Translation in personal crises: Opportunities for wearables design. \textit{Proceedings of the 14th International Conference on Information Systems for Crisis Response And Management}. 266-279. ISCRAM.\\

\footnotesize{[C8]} & Hayes, J., \href{https://hdl.handle.net/2142/96755}{Dosono, B.}, Wang, Y. (2017). ``They should be convenient and strong'': Password perceptions and practices of visually impaired users. \textit{iConference 2017 Proceedings}. 445-451.\\

\footnotesize{[C7]} & Semaan, B., \href{https://dl.acm.org/authorize?N41343}{Dosono, B.}, Britton, L. (2017). Impression management in high context societies: `Saving face' with ICT. \textit{Proceedings of the 2017 ACM Conference on Computer Supported Cooperative Work and Social Computing}. 712-725. ACM.\\

\footnotesize{[C6]} & Semaan, B., Britton, L., \href{https://dl.acm.org/authorize?N41344}{Dosono, B.} (2017). Military masculinity and the travails of transitioning: Disclosure in social media. \textit{Proceedings of the 2017 ACM Conference on Computer Supported Cooperative Work and Social Computing}. 387-403. ACM.\\

\footnotesize{[C5]} & Semaan, B., Britton, L., \href{https://dl.acm.org/authorize?N41455}{Dosono, B.} (2016). Transition resilience with ICTs: `Identity awareness' in veteran reintegration. \textit{Proceedings of the 2016 CHI Conference on Human Factors in Computing Systems}. 2882-2894. ACM.\\

\footnotesize{[C4]} & \href{https://doi.org/10.9776/16285}{Dosono, B.} (2016). Patron privacy: A luxury concern for marginalized Internet users. \textit{iConference 2016 Proceedings}.\\

\footnotesize{[C3]} & \href{https://www.usenix.org/conference/soups2015/proceedings/presentation/dosono}{Dosono, B.}, Hayes, J., Wang, Y. (2015). ``I'm stuck!'': A contextual inquiry of people with visual impairment in authentication. \textit{Symposium On Usable Privacy and Security}. 151-168. USENIX Association.\\

\footnotesize{[C2]} & \href{https://doi.org/10.9776/14043}{Dosono, B.} (2014). Digital inclusion for migrant millennials: Improving the ICT landscape of Yakima Valley Schools. \textit{iConference 2014 Proceedings}. 65-75.\\

\footnotesize{[C1]} & Ko, A., \href{https://dl.acm.org/authorize?N41457}{Dosono, B.}, Duriseti, N. (2014). Thirty years of software problems in the news. \textit{Proceedings of the 7th International Workshop on Cooperative and Human Aspects of Software Engineering}. (pp. 32-39). ACM. \medskip \\

& \large \textcolor{black}{\uppercase{Juried Workshops and Curated Sessions}}\\

\footnotesize{[W6]} & 
Costa, C., \href{https://doi.org/10.1145/3768310.3807787}{Dosono, B.}, Deal, J. (2026). ``From creator to curator: A socio-technical framework for professional identity and knowledge management in the AI‑augmented IT workforce.'' \textit{Proceedings of the 2026 Special Interest Group on Management Information Systems Conference on Computers and People Research}. ACM.\\

\footnotesize{[W5]} & 
\href{https://dl.acm.org/doi/10.1145/3491101.3516504?cid=88158835957}{Dosono, B.}, Ogbonnaya-Ogburu, I., Rankin, Y., Smith, A. D. R., Toyama, K. (2022), ``Anti-racism in action: A speculative design approach to reimagining SIGCHI.'' \textit{Extended Abstracts of the 2022 Conference on Human Factors in Computing Systems}. ACM.\\

%AUTHORIZER
\footnotesize{[W4]} & Smith, A. D. R., Ahmed, A. A., Alvarado Garcia, A., \href{https://dl.acm.org/doi/10.1145/3334480.3375156?cid=88158835957}{Dosono, B.}, Ogbonnaya-Ogburu, I., Rankin, Y., To, A., Toyama, K. (2020). What's race got to do with it? Engaging in race in HCI. \textit{Extended Abstracts of the 2020 CHI Conference on Human Factors in Computing Systems}. ACM.\\

\footnotesize{[W3]} & Kiene, C., Shores, K., Chandrasekharan, E., Jhaver, S., Jiang, J. A., Dym, B., Seering, J., Gilbert, S., Lo, K., Wohn, D. Y., \href{https://dl.acm.org/authorize?N690536}{Dosono, B.} (2019). Volunteer work: Mapping the future of moderation research. \textit{Companion Publication of the 2019 Conference on Computer Supported Cooperative Work and Social Computing}. ACM.\\

\footnotesize{[W2]} & \href{https://www.usenix.org/sites/default/files/soups15_full_proceedings.pdf}{Dosono, B.} Assessing online privacy safeguards among marginalized Internet users in public libraries. \textit{Workshop on Inclusive Privacy and Security in the Proceedings of the Eleventh Symposium On Usable Privacy and Security}. USENIX. \medskip \\

\footnotesize{[W1]} & Bayo, I., Budd, J., Caidi, N., Changfoot, N., Diaz Andrade, A., \href{https://doi.org/10.9776/14223}{Dosono, B.}, Gomez, R., Quan-Haase, A., Wolske, M. (2014). Information and marginality: Ethical issues. \textit{iConference 2014 Proceedings}. \medskip \\ \pagebreak

& \large \textcolor{black}{\uppercase{Book Chapters}}\\

\footnotesize{[B3]} & \href{https://www.peterlang.com/document/1062327}{Dosono, B.}, Lam, V., Badruddin, B. (2021). A practitioner's perspective: Asian-interest sororities and fraternities. In Garcia, C., Duran, A. (2021). Moving culturally-based sororities and fraternities forward: Innovations in practice. \textit{Peter Lang Publishing}.\\

\footnotesize{[B2]} & \href{https://myersedpress.presswarehouse.com/browse/book/9781975502645/Foundations-Research-and-Assessment-of-Fraternities-and-Sororities}{Dosono, B.}, Badruddin, B., Lam, V. (2019). History of Asian American Greek-Letter Organizations. In Sasso, P., Biddix, J. P., Miranda, M. L. (2019). Foundations, research, and assessment of fraternities and sororities: Retrospective and future considerations. \textit{Stylus Publishing}.\\

\footnotesize{[B1]} & Gee, B., Seoh, H., \href{https://myersedpress.presswarehouse.com/browse/book/9781975502683/Supporting-Fraternities-and-Sororities-in-the-Contemporary-Era}{Dosono, B.} (2019). The National Asian Pacific Islander Desi American Panhellenic Association. In Sasso, P., Biddix, J. P., Miranda, M. L. (2019). Supporting fraternities and sororities in the contemporary era: Advancements in practice. \textit{Myers Education Press}.\medskip \\ 

& \large \textcolor{black}{\uppercase{Magazine Articles}}\\

\footnotesize{[M2]} & {Race in HCI Collective, Smith, A. D. R., Alvarado Garcia, A., Arawjo, I., Bennett, A., Braswell, K., \href{https://dl.acm.org/doi/10.1145/3477097?cid=88158835957}{Dosono, B.}, Eglash, R., Ford, D., Gardner, D., Goddard, S., Nias, J.,  Passmore, C., Rankin, Y., Rizvi, N., Scott, C. F., Thomas, J., To, A., Ogbonnaya-Ogburu, I. F., Wong-Villacres, M.} (2021). Keepin' it real about race in HCI. ACM. \textit{Interactions Magazine}. 28-33.\\

\footnotesize{[M1]} & \href{https://web.archive.org/web/20240726035655/https://issuu.com/afa1976/docs/afa-perspectives-2019-issue4-final-nobleed}{Dosono, B.} (2020). Identity work in online fraternal spaces. \textit{Association of Fraternity/Sorority Advisors Perspectives}. 29-31. \medskip \\

& \large \textcolor{black}{\uppercase{Posters}}\\

% National prevalence of atopic dermatitis by insurance type and age in the United States

% Emergency department utilization for atopic dermatitis across insurance type and geography in the United States

% Geographic variation in atopic dermatitis burden, care quality, and provider access across the United States

\footnotesize{[P8]} & Heath, C. R., \href{https://eposters.aad.org/abstracts/60940}{Dosono, B.}, Shi, V. Y., Soung, J., Smith Begolka, W., Atwater, A. R., Pierce, E. J., Bacci, E., Correll, J. R., Constantine, M. L., Chovatiya, R. (2025). Differences in health care access and utilization by race and ethnicity in patients experiencing atopic dermatitis flares. \textit{American Academy of Dermatology}.\\

\footnotesize{[P7]} & Heath, C. R., \href{https://doi.org/10.25251/skin.9.supp.518}{Dosono, B.}, Shi, V. Y., Soung, J., Smith Begolka, W., Atwater, A. R., Pierce, E. J., Bacci, E., Correll, J. R., Constantine, M. L., Chovatiya, R. (2024). Race and ethnicity related variations in the social impact and stigma of atopic dermatitis among adults with AD: US-based patient survey. \textit{SKIN The Journal of Cutaneous Medicine}.\\

\footnotesize{[P6]} & Heath, C. R., \href{https://skinofcolorupdate.com/posters/}{Dosono, B.}, Shi, V. Y., Smith Begolka, W., Atwater, A. R., Pierce, E. J., Correll, J. R., Bacci, E. D., Constantine, M. L., Chovatiya, R. (2024). Variability in skin tone changes by race and ethnicity among US adults with atopic dermatitis. \textit{Skin of Color Update}.\\

\footnotesize{[P5]} & Akter, T., \href{https://www.usenix.org/sites/default/files/soups2019posters-akter.pdf}{Dosono, B.}, Ahmed, T., Kapadia, A., Semaan, B. (2019). Privacy implications of human intelligence powered assistive tools for visually impaired people. \textit{CHI 2019 Workshop on Bridging the Gap Between AI and HCI}.\\

\footnotesize{[P4]} & Figueroa, J., Sullivan, J., Grimaldi, V., \href{https://www.ideals.illinois.edu/handle/2142/100251}{Dosono, B.} (2018). Finding a future beyond the field: Exploring ICT-mediated practices of student athletes. \textit{iConference 2018 Proceedings}.\\

\footnotesize{[P3]} & \href{https://dryhootchpartners4health.org/wp-content/uploads/2017/09/Warrior-Summit-Program.pdf}{Dosono, B.}, Lee, J., Britton, L., Dobreski, B., Bratt, S., Peterman, G., Bova, K., Sharma, K., Semaan, B. (2017). Transition resilience amongst veterans. \textit{Wisconsin Warrior Summit}.\\

\footnotesize{[P2]} & \href{https://doi.org/10.9776/16575}{Dosono, B.}, Britton, L., Semaan, B. (2016). Regaining normalcy after war: ICT-enabled `Transition resilience' in veterans and refugees. \textit{iConference 2016 Proceedings}.\\

\footnotesize{[P1]} & \href{https://youtu.be/i5US90lHIac}{Dosono, B.}, Huynh, W., Liu, K., Lu, W. (2012). vTracker: Volunteer management web application. University of Washington Information School Capstone Fair. \textbf{Audience Choice Award}. \medskip \\

& \large \textcolor{black}{\uppercase{Doctoral Consortia}}\\

\footnotesize{[DC5]} 
& \href{https://web.archive.org/web/20200229145141/https://hicss.hawaii.edu/doctoral-consortium/}{Dosono, B.} (2019). Moderating identity work in online communities: The case of Asian American and Pacific Islanders on Reddit. \textit{Hawaii International Conference on System Sciences}.\\

\footnotesize{[DC4]} & \href{https://web.archive.org/web/20210309183350/https://aoir2018.sched.com/event/HPAQ/doctoral-colloquium}{Dosono, B.} (2018). Online identity work: The case of Asian Americans and Pacific Islanders on Reddit. \textit{Association of Internet Researchers}.\\

\footnotesize{[DC3]} & \href{https://tapiaconference.cmd-it.org/wp-content/uploads/2020/06/Tapia-Conference-2018-Program.pdf}{Dosono, B.} (2018). AAPI identity work on Reddit. \textit{Richard Tapia Celebration of Diversity in Computing}. ACM.\\

\footnotesize{[DC2]} & \href{https://web.archive.org/web/20180329142759/http://ischools.org/the-iconference/program/doctoral-colloquium/2018-doctoral-colloquium/}{Dosono, B.} (2018). Identity work on Reddit: Social support and collective action of Asian Americans and Pacific Islanders. \textit{iConference 2018 Proceedings}.\\

\footnotesize{[DC1]} & \href{https://dl.acm.org/authorize?N42808}{Dosono, B.} (2018). AAPI identity work on Reddit: Toward social support and collective action. \textit{Proceedings of the International Conference on Supporting Group Work}. ACM. \medskip \\

& \large \textcolor{black}{\uppercase{Technical Reports}}\\

% & \footnotesize{[R4]} & Biegel, B., \href{https://www.nasa.gov/digitalstrategy}{Dosono, B.}, Smith, T., Wang, M. (2019). Digital transformation media review. NASA. (Forthcoming)\\

\footnotesize{[T3]} & \href{https://web.archive.org/web/20201119093749/https://cdn.ymaws.com/www.afa1976.org/resource/resmgr/guides/afa-2019-resourceguide-napa-.pdf}{Dosono, B.}, Gee, B., Seoh, H. (2019). The National Asian Pacific Islander Desi American Panhellenic Association Resource Guide. Association of Fraternity/Sorority Advisors.\\

\footnotesize{[T2]} & Ganghadaran, S., \href{https://www.newamerica.org/oti/policy-papers/virtually-unused/}{Dosono, B.}, Ngu, K. (2013). Virtually unused: Virtual private networks and public internet users. New America Foundation.\\

\footnotesize{[T1]} & \href{https://web.archive.org/web/20220701074124/https://expo.uw.edu/expo/apply/238/proceedings/offering_session/431.pdf}{Dosono, B.} (2012). Digital inclusion: An action plan for the City of Seattle. University of Washington Undergraduate Research Symposium. \medskip \\

& \large \textcolor{black}{\uppercase{Commentary}}\\
\footnotesize{[CO4]} & Smith, A. D. R., Alvarado Garcia, A., \href{https://web.archive.org/web/20230924193719/https://sigchi.org/sigchi-equity-talks-10-race-sigchi/}{Dosono, B.}, Passmore, C., Ogbonnaya-Ogburu, I. F., Wong-Villacres, M., Kumar, N. (2021). SIGCHI Equity Talks \#10: Race \& SIGCHI. \textit{ACM}.\\

\footnotesize{[CO3]} & \href{https://web.archive.org/web/20151020091932/https://theinformation.ischool.uw.edu/wp/2014/04/diy-for-cya-protecting-your-privacy/}{Dosono, B.} (2014). DIY for CYA: Protecting your privacy. \textit{The Information}.\\

\footnotesize{[CO2]} & \href{https://www.newamerica.org/insights/fiber-to-the-classroom/}{Dosono, B.} (2013). Fiber to the classroom. \textit{Open Technology Institute}.\\

\footnotesize{[CO1]} & \href{https://uwartsci.wordpress.com/2011/11/25/importance-of-philanthropic-investment-for-the-next-150/}{Dosono, B.} (2011). 
Importance of philanthropic investment for UW's next 150 years. \textit{Beyond the Quad}.\\\\

\sout{\hfill} 
& \par \Large \textcolor{black}{\uppercase{Speaking\hspace{6pt} \sout{\hfill}}} \medskip \\

& \large \textcolor{black}{\uppercase{Invited Talks}}\\

\footnotesize{2025} & \href{https://www.ebayinc.com/company/be-for-everyone/}{Dosono, B.} Asian Employees at eBay Community of Inclusion. ``Red envelope meets rewards: Travel hacks for the new year.''\\

\footnotesize{2023} & \href{https://www.ebayinc.com/}{Dosono, B.} eBay AI Conference. ``Integrating the customer perspective in eBay's generative artificial intelligence design sprint.''\\

\footnotesize{2022} & \href{https://www.facebook.com/100080345041724/videos/399277394963426}{Dosono, B.} University of the Philippines Diliman, College of Education. ``STEM appreciation for lifelong application: Start UP the STEM star in you!''\\

\footnotesize{2019} & \href{https://news.syr.edu/blog/2019/03/22/celebrate-asian-american-and-pacific-islander-heritage-month-this-april/}{Dosono, B.} Syracuse University, Office of Multicultural Affairs. ``Decolonizing Asian American institutions.''\\

\footnotesize{2018} & \href{https://web.archive.org/web/20220125203815/https://cs.colgate.edu/cs/events/151/}{Dosono, B.} Colgate University, Department of Computer Science. ``Of shadow bans and sock puppets: Unraveling the deliberation and moderation of identity work on Reddit.''\\

\footnotesize{2017} & \href{https://www.sis.pitt.edu/i3/i3-cohorts/2017/schedule.html}{Dosono, B.} University of Pittsburgh, iSchool Inclusion Institute. ``Exploring Asian American and Pacific Islander identity work on Reddit.''\\

\footnotesize{2017} & Semaan, B., Britton, L., \href{https://bit.ly/CornellTalk}{Dosono, B.}, Bratt, S. Cornell University, Intercultural Communication Lab. ``Transition resilience with ICTs: The case of veteran re-integration.'' \medskip \\

& \large \textcolor{black}{\uppercase{Keynotes}}\\

\footnotesize{2026} & \href{https://sigmapsizeta.org/}{Keynote Speaker}, ``Leadership for every season.'' Sigma Psi Zeta Sorority National Convention\\

\footnotesize{2025} & \href{https://issuu.com/deltaphilambda/docs/dfl_national_convention_recap_report_2025/6}{Keynote Speaker}, ``Punctuate your life with a legacy of light.'' Delta Phi Lambda Sorority National Convention\\

\footnotesize{2024} & \href{https://www.chisigmaalpha.org/}{Keynote Speaker}, ``Growing social capital through social influence and social excellence.'' Chi Sigma Alpha Sorority and Chi Sigma Tau Fraternity Joint National Convention\\

\footnotesize{2023} & \href{https://youtu.be/xVtNAAYKqtg}{Keynote Speaker}, ``Leading with flavor: Sinanglaw for the soul.'' Santa Maria Ilocos Sur Association of Northern California 34th Anniversary and Coronation\\

\footnotesize{2021} & \href{https://bit.ly/subtlecscwtraits}{Keynote Speaker}, ``Dialogue on diaspora: Engaging Asianness beyond ‘Subtle Asian Traits.''' Subtle CSCW Traits: Tensions Around Identity Formation and Online Activism in the Asian Diaspora\\

\footnotesize{2013} & \href{https://youtu.be/uz1tukrR-7E}{Commencement Speaker}, UW Filipino American Student Association Graduation \\

\footnotesize{2012} & \href{https://youtu.be/WMPhe6H7yiM}{Keynote Speaker}, UW Spring Leadership and Service Symposium\\

\footnotesize{2012} & \href{https://ischool.uw.edu/news/2016/12/bryan-dosono-informatics-student-speaks-boeing-scholarship-breakfast}{Keynote Speaker}, UW Boeing Donor Scholarship Breakfast\\

\footnotesize{2010} & \href{https://ischool.uw.edu/about/leadership/founding-board}{Keynote Speaker}, UW Information School Founding Board Luncheon\\

\footnotesize{2011} & \href{https://youtu.be/5d2X0lZ9qwY}{Orientation Speaker}, UW All iSchool Welcome\\

\footnotesize{2008} & \href{https://youtu.be/5gt7nFRgkac}{Commencement Speaker}, Wapato High School Valedictorian Address \medskip \\

& \large \textcolor{black}{\uppercase{Lectures}}\\

\footnotesize{2022} & 
\href{https://docs.google.com/document/d/1zYOJm0msLRDsRf0cy98hJG2_zvaByd_6jiJ_JYdQWVs/edit}{Guest Lecturer}, ``Regulation and content moderation of online communities,'' SI 529: Online Communities, University of Michigan School of Information\\

\footnotesize{2022} & 
\href{https://drive.google.com/file/d/1284s_zvbBLQtUmoBzizW42yNGqyAllCt/view?usp=sharing}{Guest Lecturer}, ``Decolonizing virtual spaces: Large-scale orchestration of national representation in r/Place,'' TVR 320: Topics in Media Technology, Ithaca College School of Communications\\

\footnotesize{2018} & 
\href{https://bit.ly/IST449}{Guest Lecturer}, ``Understanding the user,'' IST 449: Human-Computer Interaction, Syracuse University School of Information Studies\\

\footnotesize{2017} & 
\href{https://bit.ly/AAA_101}{Guest Lecturer}, ``Technoscapes: Flows of information and technology,'' AAA 101: Introduction to Asian and Asian American Studies, Syracuse University College of Arts and Sciences\medskip \\

& \large \textcolor{black}{\uppercase{Courses}}\\

\footnotesize{2016} & 
\href{https://drive.google.com/file/d/0B7pKGZ82YxcVX1Y3aUdDXzV0Umc/view?usp=sharing&resourcekey=0-3bEVsEyqUwEubgH6EXgtDg}{Teaching Assistant}, IST 830: Theories of Digital Technology, Syracuse University School of Information Studies\\

\footnotesize{2015} & 
\href{https://coursecatalog.syracuse.edu/}{Teaching Assistant}, IST 719: Information Visualization, Syracuse University School of Information Studies\\

\footnotesize{2014} & 
\href{http://coursecatalog.syr.edu/}{Teaching Assistant}, IST 444: Information Reporting and Presentation, Syracuse University School of Information Studies\\

\footnotesize{2013} & 
\href{http://coursecatalog.syr.edu/}{Teaching Assistant}, IST 668: Social Web Technologies, Syracuse University School of Information Studies\\

\footnotesize{2011} & 
\href{https://www.washington.edu/students/crscat/genst.html}{Teaching Assistant}, GEN ST 349: Digital Storytelling and Community Leadership,  University of Washington College of Arts and Sciences\medskip \\

& \large \textcolor{black}{\uppercase{Panels}}\\
\footnotesize{2025} &
\href{https://afa1976.secure-platform.com/site/gallery?roundId=82021}{Moderator}, ``When APIDA voices lead: Lessons from 20 years of NAPA leadership.'' Association of Fraternity and Sorority Advisors Annual Meeting\\
%https://archive.ph/g2HTy
%https://archive.ph/hOpiZ
\footnotesize{2024} &
\href{https://aaari.info/24-05-17symposium/}{Discussant}, ``Belonging and connectedness of Asian American Greek-Letter Organizations (AAGLOs) at Asian American and Native American Pacific Islander-Serving Institutions (AANAPISIs).'' City University of New York School of Law Asian American / Asian Research Institute Symposium.\\

\footnotesize{2023} &
\href{https://web.archive.org/web/20230826203812/https://www.leadershipconvention.org/workplace-visionaries-track}{Discussant}, ``Unspoken expectations: How to boldly navigate complex business landscapes.'' National Association of Asian American Professionals Leadership Convention.\\

\footnotesize{2022} & 
\href{https://drive.google.com/file/d/187KVJ4FccmrYuKKrR3jHLQMmVObZv3VA/view?usp=sharing}{Discussant}, ``Careers in UX.'' University of Michigan School of Information, Introduction to Interaction Design.\\

\footnotesize{2022} & 
\href{https://web.archive.org/web/20230726033714/https://www.aflv.org/page/NCGLC}{Discussant}, ``National Cultural Greek Leadership Conference Town Hall.'' Association of Fraternal Leadership and Values.\\

\footnotesize{2021} & 
\href{https://web.archive.org/web/20210621134003/https://www.washington.edu/uwmcnair/annual-mcnair-conference-2/2021-conference-program/}{Discussant}, ``Fireside chat with STEM graduates.'' UW Gabriel E. Gallardo Research, Student Leadership, and Advocacy Symposium.\\

\footnotesize{2021} & \href{https://web.archive.org/web/20211201001749/https://www.lsampalumni.com/uploads/1/3/4/9/134987031/2020_-_2021_nala_report_.pdf}{Discussant}, ``Lifelong learning through the mentoring process.'' Pacific Northwest Louis Stokes Alliances for Minority Participation Conference of Oregon State University.\\

\footnotesize{2018} & \href{https://www.facebook.com/events/170505843576915/}{Discussant}, ``Diversity and inclusion in the workforce.'' SU Professional Fraternity Council.\\

\footnotesize{2015} & \href{https://web.archive.org/web/20210326175437/https://www.mortarboard.org/Docs/2015\%20CONFERENCE\%20PROGRAM.pdf}{Discussant}, ``Planning to go to grad school? Apply for a Mortar Board national fellowship!'' Mortar Board National Conference. \\

\footnotesize{2014} & \href{https://web.archive.org/web/20150129171123/http://7thannualconferenceonequity2014.sched.org/list/descriptions/}{Discussant}, ``Disruption, inclusion, and exclusion in virtual and geographic spaces.'' 7th Annual Conference on Equity and Social Justice.\\

\footnotesize{2013} & \href{https://www.washington.edu/regents/meetings/2013/meeting-minutes-for-2013/minutes-january-10-2013}{Discussant}, ``Student engagement at the University of Washington.'' UW Board of Regents.\\

\footnotesize{2012} & \href{https://www.facebook.com/events/410710345657255/}{Moderator}, ``Break the bamboo ceiling: Opportunities for incoming Asian American students.'' UW First Year Programs Dawg Daze.\medskip \\

& \large \textcolor{black}{\uppercase{Programs}}\\
\footnotesize{2025} &
\href{https://kplsorority.org/}{Workshop Presenter}, ``Globetrotter’s guide to travel hacking: Maximizing rewards from points and miles.'' Kappa Phi Lambda Sorority National Conference.\\

\footnotesize{2025} &
\href{https://www.instagram.com/p/DF_iBenK9ga/}{Workshop Presenter}, ``Writing for busy leaders: Practical communication strategies for the attention economy.'' Northeast Greek Leadership Association Annual Conference.\\

\footnotesize{2023} &
\href{https://www.instagram.com/p/CxiqWamujW2/}{Workshop Presenter}, ``Catalyzing alumni engagement from milestone anniversaries: A walkthrough of lasting landmarks and living legacies across 5, 10, 20, and 40-year fraternal reunions.'' Cultural Greek Leadership Conference at the University of Pennsylvania.\\

\footnotesize{2022} &
\href{https://apicyakima.org/2022/02/22/march-brain-trust-meeting/}{Workshop Presenter}, ``How to finance your education.'' Asian Pacific Islander Coalition of Yakima.\\

\footnotesize{2021} &
\href{https://www.library.illinois.edu/slc/news-events/national-archives-conference/2021-schedule-of-events/}{Workshop Presenter}, ``Archiving Asian American Greek-letter organization history: A decolonial praxis.'' National Archives Conference for Fraternities and Sororities.\\

\footnotesize{2021} &
\href{https://newsroom.unl.edu/announce/trio-ubms/11966/73616}{Workshop Presenter}, ``Power in the polish: Enhancing your personal brand.'' Upward Bound Math and Science Program at the University of Nebraska–Lincoln.\\

\footnotesize{2021} &
\href{https://web.archive.org/web/20210315001355/https://www.maasuls2021.org/workshops}{Workshop Presenter}, ``Affinities of affiliation: Review, relevance, and research into Asian American Greek-Letter Organizations.'' Midwest Asian Pacific Islander and Desi American Student Union Leadership Summit at the University of Missouri.\\

\footnotesize{2020} & \href{https://uwaablog.wordpress.com/wp-content/uploads/2018/05/uw-lsamp-one-pager-4.pdf}{Workshop Presenter}, ``Bridge to the doctorate.'' Pacific Northwest Louis Stokes Alliance for Minority Participation (LSAMP) at the University of Washington.\\

\footnotesize{2018} & \href{https://web.archive.org/web/20190722125246/http://www.akdphi.org/workshops}{Workshop Presenter}, ``Points, perks, partners: A frequent flyer's ultimate guide to travel hacking.'' alpha Kappa Delta Phi International Sorority Convention.\\

\footnotesize{2018} & \href{https://web.archive.org/web/20240910070425/https://issuu.com/afa1976/docs/afaam-2018-programbook-final-noblee}{Workshop Presenter}, ``The emergence and institutionalization of Asian American Greek Letter Organizations.'' Association of Fraternity/Sorority Advisors Annual Meeting.\\

\footnotesize{2017} & \href{https://suwise.syr.edu/}{Workshop Presenter}, ``Using social media to enhance your research.'' Women in Science and Engineering Program at Syracuse University.\\

\footnotesize{2016} & \href{https://web.archive.org/web/20160302043700/http://www.ecaasu2016.org/}{Workshop Presenter}, ``When sh*t gets racist: Furthering solidarity in fraternity \& sorority.'' East Coast Asian American Student Union Conference at Rutgers University.\\

\footnotesize{2012} & \href{https://shaping.wsu.edu/}{Workshop Presenter}, ``Overcoming barriers to college.'' Shaping High School Asian Pacific Islanders for the Next Generation Conference at Washington State University.\\

\footnotesize{2011} & \href{https://www.washington.edu/dreamproject/}{Workshop Presenter}, ``About the Elks National Foundation Most Valuable Student Competition.'' Dream Project Scholarship Weekend Kickoff at the University of Washington.\medskip \\ \pagebreak

& \large \textcolor{black}{\uppercase{Podcasts and Web Series}}\\
\footnotesize{2024} &
\href{https://zencastr.com/z/MDerKjSE}{Dosono, B.}, Francis, E. (2024). Episode Pi, NAPA with Bryan Dosono. \textit{Ethocast: Leadership to the Letter}.\\

\footnotesize{2024} &
\href{https://podcast.userinterviews.com/episodes/141-the-chaos-theory-of-event-networking-with-bryan-dosono-of-ebay}{Dosono, B.}, May, E., Guest, C. (2024). The chaos theory of event networking. \textit{Awkward Silences}.\\

\footnotesize{2023} &
\href{https://unsolicitedux.substack.com/p/s1e12-bryan-dosono-conference-culture}{Dosono, B.}, Kietzman, J. (2023). Conference culture. \textit{Unsolicited UX Podcast}.\\

\footnotesize{2023} &
\href{https://podcasters.spotify.com/pod/show/incredipaul/episodes/Episode-36-Prioritizing-Wellness-in-STEM-w-Bryan-Dosono--PhD-e27qo7c}{Dosono, B.}, Faronbi, P. (2023). Prioritizing wellness in STEM. \textit{IncrediPaul Podcast}. \\

\footnotesize{2021} &
\href{https://www.youtube.com/watch?v=CPGFnCFnm1s&ab_channel=UPSLIS}{Dosono, B.}, Apolinario, R. R., Dorado, D. A., Reyes, D., Surmieda, J. (2021). Opportunities with an information science course. \textit{Coffee Break: Reflections and Conversations, University of the Philippines School of Library and Information Studies}. \\

\footnotesize{2021} &
Ogbonnaya-Ogburu, I. F., Adriana, A., Wong-Villacres, M., \href{https://www.youtube.com/watch?v=n4El4VcPcVQ&list=PLqhXYFYmZ-VdgN7nr6KoCgtsT5x_Owr2Q&index=10&ab_channel=ACMSIGCHI}{Dosono, B.}, Smith, A. D. R. (2021). Race \& SIGCHI. \textit{SIGCHI Equity Talks}. \\

\footnotesize{2021} &
\href{https://anchor.fm/honestly-asian-greeks/episodes/Episode-1-History-of-AAGLOs-eok3em}{Dosono, B.}, Badruddin, B., Lam, V., Wang, C. (2021). History of AAGLOs. \textit{Honestly, Asian Greeks Podcast}. \medskip \\

& \large \textcolor{black}{\uppercase{Hosting}}\\

\footnotesize{2019} & \href{https://aflv.org/uifi}{Facilitator}, North American Interfraternity Conference Undergraduate Interfraternity Institute\\

\footnotesize{2014} & \href{https://www.facebook.com/events/1495108147408350/}{Master of Ceremonies}, SU Elements of Hip Hop Show\\

\footnotesize{2012} & \href{https://www.washington.edu/omad/2012/05/14/undergraduates-to-present-research-at-20th-annual-pacific-northwest-mcnaireipgo-map-research-conference-may-17-19/}{Master of Ceremonies}, 20th Annual Pacific Northwest McNair Program / Early Identification Program / Graduate Opportunities and Minority Achievement Program Research Conference\\

\footnotesize{2012} & \href{https://youtu.be/WMPhe6H7yiM}{Master of Ceremonies}, UW Information School Dean's Club Dinner\\\\

\sout{\hfill} 
& \par \Large \textcolor{black}{\uppercase{Service\hspace{6pt} \sout{\hfill}}} \medskip \\

& \large \textcolor{black}{\uppercase{Capacity Building}}\\
\footnotesize{2024} & \href{https://www.pcori.org/research-results/2023/paving-way-towards-meaningful-partnerships-fostering-regional-pcor-enhance-eczema-outcomes}{Project Advisor}, Eugene Washington PCORI Engagement Award Program (funded by the Patient-Centered Outcomes Research Institute): ``Paving the way towards meaningful partnerships: Fostering regional PCOR to enhance eczema outcomes''\\

\footnotesize{2024} & \href{https://www.cdc.gov/chronic-disease-educational-awareness/php/funding/building-capacity-awardees.html}{Project Advisor}, Building Capacity for Chronic Disease Education and Awareness Grant (funded by the Centers for Disease Control and Prevention): ``Atopic dermatitis is more than a skin disease: Raising awareness and improving care project''\\

\footnotesize{2023} & \href{https://www.pcori.org/research-results/2019/mag-pcor-muna-tayo-nationwide-capacity-building-filipino-americans-engage-pcor-and-cer}{Project Advisor}, Filipino American Research Hub (funded by the Patient-Centered Outcomes Research Institute): ``Mag-PCOR muna tayo: Nationwide capacity building for Filipino-Americans to engage in patient-centered outcomes research and comparative effectiveness research'' \medskip \\

& \large \textcolor{black}{\uppercase{Research Councils}}\\
\footnotesize{2023} & \href{https://youtu.be/z_kgBHkfCiE}{Advisory Board Member}, Center for Filipino American Health\\

\footnotesize{2023} & \href{https://nationaleczema.org/about-nea/patient-caregiver-research-advisory-council/}{Advisory Board Member}, National Eczema Association Patient and Caregiver Research Advisory Council\\

\footnotesize{2023} & \href{https://www.userinterviews.com/}{Advisory Board Member}, User Interviews \medskip \\

& \large \textcolor{black}{\uppercase{Civic Engagement}}\\ 

\footnotesize{2019} & \href{https://apiavote.org/initiatives/youth-and-ambassadors/}{Advisor}, Asian Pacific Islander American Vote Youth Advisory Board\\

\footnotesize{2015} & \href{https://obamawhitehouse.archives.gov/blog/2015/09/04/white-house-initiative-aapis-selects-23-young-leaders-serve-2015-2016-e3-ambassadors}{Ambassador}, White House Initiative on Asian Americans and Pacific Islanders\\

\footnotesize{2011} & \href{https://web.archive.org/web/20150911093548/https://ischool.uw.edu/alumni/impact-stories/informatics-grad-and-husky-promise-student-aims-deliver-it-resources}{Commissioner}, City of Seattle Community Technology Advisory Board \medskip \\

& \large \textcolor{black}{\uppercase{Employee Resource Groups}}\\

\footnotesize{2026} & 
\href{https://inclusion.twdc.com/}{{Pamilya at Disney}}, Planning Committee\\ 

\footnotesize{2025} & 
\href{https://www.asianleadersalliance.com/}{{Asian Leaders Alliance}}, Brain Trust\\ 

\footnotesize{2023} & 
\href{https://www.tiktok.com/@ebaystories/video/7334050647136013614}{{Asian Employees at eBay}}, New York City Site Lead\\

\footnotesize{2019} & 
\href{https://web.archive.org/web/20200221070731/https://www.airbnb.com/diversity/belonging}{{Asians@ Airbnb}}, Bayanihan Filipino Night Market Volunteer \medskip \\

& \large \textcolor{black}{\uppercase{Technical Program Committees and Reviewing}}\\

\footnotesize{2024} & 
\href{https://dis.acm.org/}{Reviewer}, ACM Designing Interactive Systems\\

\footnotesize{2024} & 
\href{https://www.computer.org/csdl/magazine/sp}{Reviewer}, IEEE Security \& Privacy\\

\footnotesize{2024} & 
\href{https://www.sciencedirect.com/journal/international-journal-of-disaster-risk-reduction}{Reviewer}, International Journal of Disaster Risk Reduction\\

\footnotesize{2022} & 
\href{https://uxpa2024.org/conference-committee/}{Conference Chair}, User Experience Professionals Association International Conference\\

\footnotesize{2021} & 
\href{https://dl.acm.org/journal/tsc}{Reviewer}, ACM Transactions on Social Computing\\

\footnotesize{2021} & \href{https://lsmrce.org/events/annual/2021-annual/2021-conference-with-gratitude.aspx}{Poster Judge}, Louis Stokes Midwest Regional Center of Excellence Annual Conference\\

\footnotesize{2021} & 
\href{https://dl.acm.org/journal/tochi}{Reviewer}, ACM Transactions on Computer-Human Interaction\\

\footnotesize{2019} & \href{https://web.archive.org/web/20260703133254/https://hicss.hawaii.edu/}{Reviewer}, Hawaii International Conference on System Sciences\\

\footnotesize{2019} & \href{https://uist.acm.org/uist2019/}{Reviewer}, ACM Symposium on User Interface Software and Technology\\

\footnotesize{2018} & \href{https://chi2018.acm.org}{Session Chair \& Student Volunteer}, ACM Conference on Human Factors in Computing Systems\\

\footnotesize{2018} & \href{https://group.acm.org/conferences/group18/index.html}{Student Volunteer}, ACM International Conference on Supporting Group Work\\

\footnotesize{2017} & \href{https://sigchi.org/}{Student Volunteer}, ACM SIGCHI Executive Committee\\

\footnotesize{2017} & \href{https://chi2017.acm.org/}{Reviewer \& Student Volunteer}, ACM Conference on Human Factors in Computing Systems\\

\footnotesize{2016} & \href{https://cscw.acm.org/}{Reviewer}, Computer-Supported Cooperative Work and Social Computing\\

\footnotesize{2015} & \href{https://www.ischools.org/iconference}{Reviewer \& Student Volunteer Captain}, iConference\\

\footnotesize{2014} & \href{https://www.usenix.org/sites/default/files/soups14_proceedings.pdf}{Reviewer}, Symposium On Usable Privacy and Security \medskip \\

& \large \textcolor{black}{\uppercase{University Departments}}\\

\footnotesize{2019} & \href{https://dailyorange.com/2019/04/su-alum-deliver-lecture-industry-experience-cultural-identity-aapi-month/}{Co-Chair}, SU Office of Multicultural Affairs Asian American Pacific Islander Heritage Month\\

\footnotesize{2017} & \href{https://ischool.syr.edu/}{Doctoral Representative}, SU iSchool Hiring Committee\\

\footnotesize{2015} & \href{https://web.archive.org/web/20180119000045/https://gradresearch.syr.edu/symposium/}{Organizer}, SU Graduate Forum on Research Methodologies\\

\footnotesize{2014} & \href{https://gradorg.syr.edu/senate/committees/}{Graduate Student Representative}, SU Graduate Council\\

\footnotesize{2014} & \href{https://gradorg.syr.edu/senate/committees/}{Chair}, SU Graduate Senate Academic Affairs Committee\\

\footnotesize{2014} & \href{https://universitysenate.syr.edu/}{Graduate Student Representative}, SU Senate\\

\footnotesize{2014} & \href{https://web.archive.org/web/20180119000045/https://gradresearch.syr.edu/symposium/}{Organizer}, SU Graduate Research Symposium\\

\footnotesize{2014} & \href{https://ischool.syr.edu/}{Doctoral Representative}, SU iSchool Personnel Committee\\

\footnotesize{2013} & \href{https://ischool.syr.edu/}{Doctoral Representative}, SU iSchool Faculty Committee\\

\footnotesize{2013} & \href{https://dailyorange.com/2013/12/su-app-challenge-to-announce-winners-thursday/}{Organizer}, SU App Challenge Hackathon\\

\footnotesize{2013} & \href{https://www.washington.edu/omad/2014/05/09/no-longer-invisible-bryan-dosono/}{Student Representative}, UW Office of Minority Affairs and Diversity Student Advisory Board\\

\footnotesize{2013} & \href{https://depts.washington.edu/uwdrs/current-students/accommodations/notetaking/}{Notetaking Volunteer}, UW Disability Services Office\\

\footnotesize{2012} & \href{https://ischool.uw.edu/current/career-services}{Student Volunteer}, UW Information School Research Fair\\

\footnotesize{2012} & \href{https://web.archive.org/web/20130104065107/https://ischool.uw.edu/news/2012/11/annual-ischool-research-fair-showcases-faculty-and-student-work}{Student Volunteer}, UW Information School Career Fair\\

\footnotesize{2011} & \href{https://ischool.uw.edu/about/leadership}{Undergraduate Student Representative}, UW Informatics Program Committee\\

\footnotesize{2009} & \href{https://en.wikipedia.org/wiki/The_Daily_of_the_University_of_Washington}{Undergraduate Student Representative}, UW Student Publications Board \medskip \\ \pagebreak

& \large \textcolor{black}{\uppercase{Student Affairs}}\\
\footnotesize{2025} & \href{https://main.saseconnect.org/pro/awards}{Judge}, Society of Asian Scientists and Engineers (SASE) Leadership Awards\\

\footnotesize{2024} & \href{https://aaci.org/}{Judge}, Asian Americans for Community Involvement (AACI) Growing Up in America Art Contest\\

\footnotesize{2024} & \href{https://apiascholars.org/}{Reviewer}, APIA Scholars Scholarship Program\\

\footnotesize{2022} & \href{https://scholarworks.wm.edu/oracle/editorialboard.html}{Reviewer}, Oracle: The Research Journal of the Association of Fraternity/Sorority Advisors\\

\footnotesize{2021} & 
\href{http://www.fgrc.com/}{Alumni Advocate}, Fraternal Government Relations Coalition\\

\footnotesize{2020} & 
\href{https://nalfo.org/nalfo-awards/}{Reviewer}, National Association of Latino Fraternal Organizations Awards Committee\\

\footnotesize{2019} & 
\href{https://www.albany.edu/studentaffairs/commission_members.shtml}{National Asian Panhellenic Council Representative}, University at Albany Commission on the Future of Greek Life\\

\footnotesize{2019} & 
\href{https://ese.syr.edu/multicultural/calendar/asian-american-and-pacific-islander-heritage-month/}{Judge}, SU Mr. Asia Male Pageant\\

\footnotesize{2017} & 
 \href{https://www.facebook.com/syracusefsa/}{Founding Advisor}, SU Filipino Student Association\\

\footnotesize{2017} & \href{https://web.archive.org/web/20241207175640/https://issuu.com/alinemagazine}{Senior Editor}, SU ALINE Magazine\\

\footnotesize{2012} & \href{https://www.fiuts.org/blog/2020/4/1/stepping-to-build-community}{President}, UW United Greek Council\\

\footnotesize{2011} & \href{https://uwlambdas.com/}{President}, UW Lambda Phi Epsilon\\

\footnotesize{2011} & \href{https://www.facebook.com/events/972221256174460/}{Judge}, UW Asian Student Commission Talent Show\\

\footnotesize{2011} & \href{https://www.dailyuw.com/news/article_da48b049-d2a0-582c-9dfb-4589755ff1e5.html}{Senate Speaker}, Associated Students of the University of Washington\\

\footnotesize{2011} & \href{https://www.dailyuw.com/features/article_107d7a3a-3bec-5989-b8ae-56bd4afd0c89.html}{Vice President}, UW Lambda Phi Epsilon\\

\footnotesize{2010} & \href{https://www.facebook.com/spepatuw/}{Founder}, UW Student Philanthropy Education Program\\

\footnotesize{2010} & \href{https://dawgdaze.fyp.uw.edu/}{Team Captain}, UW First Year Programs Dawg Daze\\

\footnotesize{2009} & \href{https://www.dailyuw.com/news/article_05df45ba-6f0b-5612-964e-ab318f36b612.html}{Membership Coordinator}, Associated Students of the University of Washington\\

\footnotesize{2009} & \href{https://web.archive.org/web/20251118013937/https://honors.uw.edu/community/grads/12_13/}{Mentor}, UW Honors Program \medskip \\

& \large \textcolor{black}{\uppercase{Community Outreach}}\\

\footnotesize{2026} & \href{https://stationeryfestival.com/}{Volunteer}, New York Stationery Festival (Forthcoming)\\

\footnotesize{2026} & \href{https://boston2026.com/}{Volunteer}, American Philatelic Society World Expo\\

\footnotesize{2023} & \href{https://web.archive.org/web/20240304010059/https://d101tm.org/district-101/2023-24-pr-team/}{Social Chair}, Toastmasters District 101\\

\footnotesize{2022} & \href{https://nationaleczema.org/research-ambassadors/}{Research Ambassador}, National Eczema Association\\

\footnotesize{2022} & \href{https://faster-steam.org/}{Historian}, Filipinx Americans in Science, Technology, Engineering, Arts, and Mathematics\\

\footnotesize{2022} & \href{https://www.instagram.com/p/CjoCaCQv9OS/}{Self Defense Demonstrator}, Pangalay Circle at Kapwa Gardens\\

\footnotesize{2022} & \href{https://www.paloaltoonline.com/news/2022/08/23/nonprofit-neighbors-abroad-to-host-international-festival-unveil-new-sign}{Self Defense Demonstrator}, Palo Alto City Hall Neighbors Abroad International Festival\\

\footnotesize{2022} & \href{https://www.instagram.com/p/Cc8jU07vENh/}{Self Defense Demonstrator}, Filipino Mental Health Initiative of San Francisco\\

\footnotesize{2016} & \href{https://www.facebook.com/events/215634702135825/}{Mental Health Summit Organizer}, National Asian American Pacific Islander Mental Health Association\\

\footnotesize{2014} & \href{https://icanshine.org/}{Youth Coach}, iCan Shine Bike Camp\\

\footnotesize{2012} & \href{https://www.dailyuw.com/news/article_de3524ce-3d5e-5dd2-8de7-5deebee463d9.html}{Volunteer Coordinator}, Be The Match\\

\footnotesize{2011} & \href{https://www.facebook.com/WalkforRice/}{Fundraising Volunteer}, Asian Counseling Referral Service Walk For Rice\\

\footnotesize{2011} & \href{https://www.spl.org}{Welcome Desk Volunteer}, Seattle Public Library\\

\footnotesize{2010} & \href{https://www.habitatskc.org/}{Computer Literacy Tutor}, Joel Nafuma Refugee Center\\

\footnotesize{2010} & \href{https://nwasianweekly.com/2010/05/asian-pacific-american-heritage-at-the-center/}{Step Performer}, Seattle Center Asian Pacific American Heritage Month Celebration\\

\footnotesize{2010} & \href{https://www.habitatskc.org/}{Construction Volunteer}, Habitat for Humanity of Seattle-King County\\

\footnotesize{2009} & \href{https://www.cancer.org/involved/fundraise/relay-for-life.html}{Fundraising Volunteer}, American Cancer Society Relay for Life\\

\footnotesize{2009} & \href{https://www.washington.edu/news/2010/04/22/student-service-and-leadership-to-be-celebrated-april-28/}{Hardware Refurbisher}, InterConnection\\

\footnotesize{2009} & \href{https://youthcare.org}{Tutor}, YouthCare\\

\footnotesize{2009} & \href{https://www.rescue.org}{Administrative Intern}, International Rescue Committee \medskip \\

& \large \textcolor{black}{\uppercase{Affiliations}}\\

\footnotesize{2023} & 
\href{https://uxpa.org/}{{User Experience Professionals Association}} (UXPA) \\

\footnotesize{2022} & 
\href{https://www.epicpeople.org/}{{Ethnographic Praxis in Industry Conference}} (EPIC) \\

\footnotesize{2022} & 
\href{https://www.invisionapp.com/future-of-work/design-leadership}{{Design Leadership Forum}} (DLF) \\

\footnotesize{2022} & \href{https://naffaa.org/}{National Federation of Filipino American Associations} (NaFFAA)\\

\footnotesize{2021} & \href{https://www.toastmasters.org/}{Toastmasters International} (TI)\\

\footnotesize{2020} & \href{https://www.legacyfma.com/team-3}{Legacy Filipino Martial Arts} (FMA)\\

\footnotesize{2018} & \href{https://www.nyas.org/}{New York Academy of Sciences} (NYAS)\\

\footnotesize{2017} & \href{https://www.sigchi.org/}{Special Interest Group on Computer-Human Interaction} (SIGCHI)\\

\footnotesize{2015} & \href{https://www.acm.org/}{Association of Fraternity/Sorority Advisors} (AFA)\\

\footnotesize{2013} & \href{https://dl.acm.org/profile/88158835957}{Association for Computing Machinery} (ACM)\\

\footnotesize{2013} & \href{https://www.ieee.org/}{Institute of Electrical and Electronics Engineers} (IEEE)\\

\footnotesize{2008} & \href{https://www.asist.org/}{Association for Information Science and Technology} (ASIS\&T) \medskip \\ \pagebreak

& \large \textcolor{black}{\uppercase{Training Institutes}}\\

\footnotesize{2026} & \href{https://web.archive.org/web/20260415072142/https://www.gilmanscholarship.org/program/gilman-foreign-policy-in-focus/}{Gilman Foreign Policy in Focus: Critical and Emerging Technology Seminar}\\

\footnotesize{2018} & \href{https://www.oii.ox.ac.uk/news-events/news/oii-sdp-cultivating-charismatic-cohorts/}{Oxford Internet Institute Summer Doctoral Programme}\\

\footnotesize{2018} & \href{https://cra.org/events/urmgradcohort/}{Computing Research Association Grad Cohort Workshop for Underrepresented Minorities + Persons with Disabilities}\\

\footnotesize{2015} & \href{https://graduateschool.syr.edu/current-students/future-professoriate-program/}{SU Future Professoriate Program Annual Conference}\\

\footnotesize{2013} & \href{https://web.archive.org/web/20240303190220/https://graduateschool.syr.edu/diversity-inclusion/}{SU Minority Graduate Student Orientation Program}\\

\footnotesize{2013} & \href{https://www.capal.org/programs/wlp/}{Conference on Asian Pacific American Leadership: Washington Leadership Program}\\

\footnotesize{2011} & \href{https://www.seattleymca.org/get-engaged-boards-commissions}{YMCA Get Engaged Program}\\

\footnotesize{2008} & \href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4167726}{Minority Scholars Engineering Program: Alliances for Learning and Vision for Underrepresented Americans} \medskip \\ 

& \large \textcolor{black}{\uppercase{Doctoral Supervision}}\\

\footnotesize{2025} & \href{https://www.linkedin.com/in/sglt/}{Sarah Tran}, Ph.D. Candidate, Pennsylvania State University, College of Information Sciences and Technology. Thesis proposal: ``Social Media as A Tool to Navigate Lived Experiences and Mental Health Challenges among Vietnamese Americans in the US.''\\

\footnotesize{2022} & \href{https://digitalcommons.njit.edu/dissertations/1594/}{Jie Cai}, Ph.D., New Jersey Institute of Technology, Ying Wu College of Computing. Thesis: ``Understanding the voluntary moderation practices in live streaming communities.'' \\ \\

\sout{\hfill} & \par \Large \textcolor{black}{\uppercase{Funding\hspace{6pt} \sout{\hfill}}} \medskip \\ 

& \large \textcolor{black}{\uppercase{Fellowships}}\\

\footnotesize{2018} & \href{https://forum2018.diglib.org/fellowship-opportunities/fellows/}{Digital Library Federation New Professional Fellowship} (\$1,000)\\

\footnotesize{2016} & \href{https://www.sis.pitt.edu/i3/phd-fellows/fellow-profiles.html}{Andrew W. Mellon Foundation iSchool Inclusion Institute Fellowship} (\$1,000)\\

\footnotesize{2016} & \href{https://www.bankofamerica.com/philanthropic/foundation.go?fnId=31}{Lloyd G. Balfour Foundation Fellowship} (\$1,000)\\

\footnotesize{2015} & \href{https://web.archive.org/web/20170822003712/https://news.syr.edu/2015/07/ischool-student-awarded-5000-mortar-board-fellowship-22021/}{Mortar Board Graduate Fellowship} (\$5,000)\\

\footnotesize{2015} & \href{https://web.archive.org/web/20170822003712/https://news.syr.edu/2015/07/ischool-student-awarded-5000-mortar-board-fellowship-22021/}{Elizabeth D. Liddy Dean's Fellowship} (\$7,000)\\

\footnotesize{2013} & \href{https://www.google.com/policyfellowship/2013fellows.html}{Google Policy Fellowship} (\$7,500)\\

\footnotesize{2013} & \href{https://www.syracuse.edu/admissions/cost-and-aid/types-of-aid/graduate-student-aid/fellowships/}{Ronald E. McNair Graduate Fellowship} (\$23,135)\\

\footnotesize{2009} & \href{https://www.washington.edu/uaa/2010/04/22/uw-celebrates-undergraduate-leadership-and-civic-engagement/}{Robert Lee Ellis Civic Fellowship} (\$12,000) \medskip \\ \pagebreak

& \large \textcolor{black}{\uppercase{Scholarships}}\\

\footnotesize{2019} & \href{https://signal.twilio.com/}{Twilio Signal Conference Scholarship} (\$1,500)\\

\footnotesize{2018} & \href{https://www.afa1976.org/foundation}{Thomas B. Jelke Graduate Scholarship} (\$300)\\

\footnotesize{2014} & \href{https://youtu.be/kFmO44rs3-c}{SU Katzer Research Fund} (\$11,000)\\

\footnotesize{2013} & \href{https://www.washington.edu/uaa/tag/mary-gates-endowment-for-students/#BryanDosono}{Bill and Melinda Gates Foundation, Mary Gates Endowment Research Scholarship} (\$4,000)\\

\footnotesize{2012} & \href{https://web.archive.org/web/20250519052345/https://expo.uw.edu/expo/apply/278/proceedings/offering_session/510}{Early Identification Program Presidential Scholarship} (\$3,500)\\

\footnotesize{2012} & \href{https://www.nsf.gov/funding/initiatives/reu}{National Science Foundation Research Experience for Undergraduates Grant} (\$6,399)\\

\footnotesize{2012} & \href{https://www.waopportunityscholarship.org/}{College Success Foundation Washington State Opportunity Scholarship} (\$1,000)\\

\footnotesize{2012} & \href{https://www.washington.edu/uaa/2013/06/28/oh-the-places-theyll-go-new-grads-and-their-plans/bryan-dosono/}{University of Washington Homecoming King Royalty Scholarship} (\$1,000)\\

\footnotesize{2011} & \href{https://ischool.uw.edu/news/2016/12/bryan-dosono-informatics-student-speaks-boeing-scholarship-breakfast}{Boeing Diversity Scholarship} (\$3,000)\\

\footnotesize{2011} & \href{https://www.washington.edu/omad/2011/05/17/assunta-ng-student-scholars-honored-at-41st-annual-eop-celebration/}{Ruth and William Gerberding Scholarship} (\$2,000)\\

\footnotesize{2011} & \href{https://lambdaphiepsilon.org/resources/\#academicachievement}{Lambda Phi Epsilon International Brother of the Year Scholarship} (\$1,500)\\

\footnotesize{2010} & \href{https://honors.uw.edu/news-archive/brief/?id=61}{Benjamin A. Gilman International Scholarship} (\$3,000)\\

\footnotesize{2010} & \href{https://web.archive.org/web/20210525151411/https://www2.ed.gov/programs/smart/index.html}{National Science and Math Access to Retain Talent Grant} (\$1,333)\\

\footnotesize{2010} & \href{https://www.washington.edu/studyabroad/students/resources/finances/scholarships/}{Washington State Global Opportunities Grant} (\$3,000)\\

\footnotesize{2008} & \href{https://web.archive.org/web/20200328042219/https://www.washington.edu/giving/recognition/rtc-2016/top-ten-lists/}{BAVA Endowed Scholarship} (\$15,036)\\

\footnotesize{2008} & \href{https://www.wsac.wa.gov/}{Washington Scholar Full Tuition Scholarship} (\$30,000)\\

\footnotesize{2008} & \href{https://www.elks.org/enf/scholars/}{Elks National Foundation Scholarship} (\$7,000)\\

\footnotesize{2008} & \href{https://www.dellscholars.org/}{Dell Scholars Foundation Scholarship} (\$20,000)\\

\footnotesize{2008} & \href{https://www.facebook.com/MabuhayFoundationinYKMValley}{Mabuhay Foundation Memorial Scholarship} (\$500)\\

\footnotesize{2008} & \href{https://www.ed.gov/grants-and-programs/grants-special-populations/grants-economically-disadvantaged-students/gaining-early-awareness-and-readiness-undergraduate-programs-gear-84334a84334s}{Gaining Early Awareness and Readiness for Undergraduate Programs Scholarship} (\$12,000) \medskip \\

& \large \textcolor{black}{\uppercase{Travel Grants}}\\

\footnotesize{2018} & \href{https://www.nsf.gov/awardsearch/show-award/?AWD_ID=1823052}{National Science Foundation ACM Richard Tapia Celebration of Diversity in Computing Conference Travel Grant} (\$1,348)\\

\footnotesize{2018} & \href{https://www.nsf.gov/awardsearch/show-award/?AWD_ID=1713738}{National Science Foundation iConference 2018 Doctoral Colloquium Travel Grant} (\$1,845)\\

\footnotesize{2018} & \href{https://cra.org/events/urmgradcohort/}{Computing Research Association Travel Grant} (\$900)\\

\footnotesize{2018} & \href{https://dl.acm.org/citation.cfm?id=3148330}{ACM GROUP Doctoral Consortium Travel Grant} (\$1,000)\\

\footnotesize{2017} & \href{https://gradorg.syr.edu/}{SU Graduate Student Organization Travel Grant} (\$900)\\

\footnotesize{2017} & \href{https://web.archive.org/web/20240817225719/https://ischool.syr.edu/dosono-to-attend-acm-turing-award-celebration/}{ACM SIGCHI 50th Celebration of the Turing Award Student Scholarship} (\$900)\\

\footnotesize{2016} & \href{https://web.archive.org/web/20250621045246/https://archive.sigchi.org/sigchi-sponsors-students-to-attend-turing-award-celebration/}{ACM SIGCHI Student Travel Grant} (\$1,500)\\

\footnotesize{2016} & \href{https://ischool.syr.edu/grants/}{SU iSchool Doctoral Travel Grant} (\$800)\\

\footnotesize{2015} & \href{https://cups.cs.cmu.edu/soups/2015/cfp.php}{Symposium on Usable Privacy and Security Travel Grant} (\$500)\\

\footnotesize{2015} & \href{https://web.archive.org/web/20191207035855/https://ischool.syr.edu/research/grants-and-awards/}{SU iSchool Doctoral Travel Grant} (\$700)\\\\

\sout{\hfill} 
& \par \Large \textcolor{black}{\uppercase{Recognition\hspace{6pt} \sout{\hfill}}} \medskip \\

& \large \textcolor{black}{\uppercase{Awards}}\\

%\footnotesize{2026} & 
%\href{https://www.toastmasters.org/education/distinguished-toastmaster}{Distinguished Toastmaster Award}\\

\footnotesize{2024} & 
\href{https://adplist.org/community-certifications/top50-dec-2024-ux-research-a39307}{Top 50 ADPList Mentor in UX Research}\\

\footnotesize{2024} & 
\href{https://cscw.acm.org/2024/index.php/awards/}{ACM CSCW Honorable Mention Award (Top 3\% of Submitted Papers)}\\

\footnotesize{2024} & 
\href{https://www.facebook.com/AFA1976/videos/1373580967342312}{Elevation in Practice (Inaugural Inclusion Award), Association of Fraternity and Sorority Advisors}\\

\footnotesize{2024} & 
\href{https://ebay.design/about#ux-research}{eBay Spot Award, Responsible AI}\\

\footnotesize{2023} & 
\href{https://www.facebook.com/PTK.Elite/posts/pfbid0334DeNzPG48z59rssnxWKtzSdgPXmRXjLGGYqxbyWtdVJtQ31cxXErfckGbbASDb7l}{Yakan Isa Promotion, Pekiti Tirsia Kali World Federation}\\

\footnotesize{2023} & 
\href{https://d101tm.org/the-luncheon-in-july/}{Toastmasters District 101 Shooting Star Award}\\

\footnotesize{2023} & 
\href{https://ebay.design/about#ux-research}{eBay Spot Award, Core Design}\\

\footnotesize{2022} & 
\href{https://www.youtube.com/watch?v=MlA4KEbI1Gw}{National Marrow Donor Program ONE Forum Service Award}\\

\footnotesize{2022} & 
\href{https://ebay.design/about#ux-research}{eBay Spot Award (2×), Design Research}\\

\footnotesize{2021} & 
\href{https://presidentialserviceawards.gov/}{AmeriCorps President's Volunteer Service Award}\\

\footnotesize{2020} & 
\href{https://cscw.acm.org/2020/awards/}{ACM CSCW Best Paper Award (Top 1\% of Submitted Papers)}\\

\footnotesize{2019} & 
\href{https://www.forbes.com/sites/forbespr/2017/09/12/forbes-under-30-scholars-program-focused-on-diversity-and-inclusion-offers-1000-college-students-access-to-2017-forbes-under-30-summit/}{Forbes Under 30 Scholar}\\

\footnotesize{2019} & 
\href{https://news.syr.edu/blog/2019/04/29/44-stars-of-excellence-awards-honor-members-of-campus-community/}{SU Office of Multicultural Affairs' Irma Almirall-Padamsee La Fuerza Community Enhancement Award}\\

\footnotesize{2019} &\href{https://news.syr.edu/blog/2019/04/29/44-stars-of-excellence-awards-honor-members-of-campus-community/}{SU Award for Excellence by an Organizational Advisor}\\

\footnotesize{2019} &
\href{https://x.com/bdosono/status/1082439167512961024}{Association for Information Systems, Hawaii International Conference on System Sciences Doctoral Fellow}\\

\footnotesize{2018} &
\href{https://www.napahq.org/2018-napa-standards-of-excellence-award-recipients/}{National APIDA Panhellenic Association Volunteer of the Year}\\

\footnotesize{2013} & \href{https://ischool.uw.edu/news/2016/12/2013-ischool-convocation-celebrates-achievement-and-community}{UW Faculty Award for Student Excellence in Informatics}\\

\footnotesize{2013} & \href{https://www.washington.edu/omad/celebration/recognition-scholarship-recipients/2013-celebration-scholarship-recipients/}{UW President's Achievement Award}\\

\footnotesize{2013} & \href{https://hub.washington.edu/whats-happening/hub-awards/}{UW Hall of Fame Inductee for Outstanding Contributions to Student Activities}\\

\footnotesize{2013} & \href{https://www.facebook.com/EthnicCulturalCenter/photos/a.10151638127531422.1073741830.124987626421/10151638128881422/}{UW Ethnic Cultural Center Director's Outstanding Leadership Award}\\

\footnotesize{2013} & \href{https://www.facebook.com/UWiSchool/posts/10151645734368695}{UW Commencement Gonfaloniere}\\

\footnotesize{2013} & \href{https://www.yakimaherald.com/news/education/school-news-sept/article_af5885a3-bcbc-5925-bb87-a84844c6d36a.html}{UW Dean's List (4×)}\\

\footnotesize{2013} & \href{https://cele.uw.edu/programs/husky-leadership-certificate/}{Husky Leadership Certificate}\\

\footnotesize{2012} & \href{https://ischool.uw.edu/capstone/projects/awards}{UW iSchool Capstone Audience Choice Award}\\

\footnotesize{2009} & \href{https://web.archive.org/web/20200328032852/https://wiki.asuw.org/index.php/Bryan_Dosono}{ASUW Employee of the Month} \medskip \\

& \large \textcolor{black}{\uppercase{Highlights}}\\
\footnotesize{2026} & \href{https://mailchi.mp/iie/april-2026-alumni-newsletter-9440759?e=36c96d11a4}{Alumni Spotlight}, May 2026 Gilman Alumni Newsletter\\

\footnotesize{2024} & \href{https://www.userweekly.com/quant-uxr-projects/}{Video of the Week}, User Weekly\\

\footnotesize{2023} & \href{https://magazine.washington.edu/feature/new-book-tells-the-story-of-the-office-of-minority-affairs-diversity/}{Notable Alumni of the Decade}, ``Revolution to Evolution: The Story of the Office of Minority Affairs \& Diversity at the University of Washington''\\

\footnotesize{2022} & \href{https://web.archive.org/web/20240829155704/https://surface.syr.edu/topdownloads.html}{Most Popular Papers (Top 10 Downloads of All Time)}, SU Research Facility and Collaborative Environment\\

\footnotesize{2022} & \href{https://www.washington.edu/omad/2023/06/14/dr-bryan-dosono-winter-2022/}{Alumni Spotlight}, UW LSAMP\\

\footnotesize{2022} & \href{https://honors.uw.edu/about/honors-60th/60th-timeline/}{Alumni Spotlight}, UW Honors Program\\

\footnotesize{2018} &
\href{https://admit.washington.edu/academics/research/}{Research Spotlight}, UW Undergraduate Research Program\\

\footnotesize{2010} &
\href{https://uwadmissions.wordpress.com/husky-promise/}{Admissions Spotlight}, UW Husky Promise Program\medskip\\

& \large \textcolor{black}{\uppercase{Honorary}}\\

\footnotesize{2012} & \href{https://orderofomega.org/}{Order of Omega}\\

\footnotesize{2011} & \href{https://www.goldenkey.org/}{Golden Key International Honor Society}\\

\footnotesize{2011} & \href{https://web.archive.org/web/20250821074323/https://depts.washington.edu/uwpbk/downloads/pbk_invitees_2011.pdf}{Phi Beta Kappa}\\

\footnotesize{2010} & \href{https://students.washington.edu/nrhh/Relevant/Active\%20Members.html}{National Residence Hall Honorary}\\

\footnotesize{2009} & \href{https://www.phietasigma.org/}{Phi Eta Sigma National Honor Society}\\

\footnotesize{2009} & \href{https://nscs.org/}{National Society of Collegiate Scholars} \medskip \\ 

& \large \textcolor{black}{\uppercase{Press}}\\

\footnotesize{2026} & \href{https://hipaa-submit.jotform.com/253496242654160}{\textit{Health Monitor Living}}, ``Eczema no longer controls our lives!''\\

\footnotesize{2025} & \href{https://nationaleczema.org/blog/how-an-analytical-mind-became-one-adults-superpower/}{\textit{National Eczema Association}}, ``How an analytical mind became this adult’s `superpower'''\\

\footnotesize{2023} & \href{https://boldjourney.com/news/meet-bryan-dosono/}{\textit{Bold Journey}}, ``Meet Bryan Dosono''\\

\footnotesize{2023} & \href{https://nationaleczema.org/wp-content/uploads/2023/10/NEA_Magazine_Fall2023_D01_Web.pdf}{\textit{NEA Magazine}}, ``NEA Ambassadors' corner: Building community over the summer''\\

\footnotesize{2023} & \href{https://waopportunityscholarship.org/get-involved/news/meet-bryan-dosono-opportunity-scholar-alum/}{\textit{Washington State Opportunity Scholarship}}, ``Meet Bryan Dosono, Opportunity Scholar alum''\\

\footnotesize{2020} & \href{https://lsmrce.org/documents/community/LSAMP-Trailblazers-Magazine-2020.pdf}{\textit{LSAMP Magazine}}, ``1000+ LSAMP innovators and trailblazers impacting the world''\\

\footnotesize{2019} & \href{https://web.archive.org/web/20211124225929/https://issuu.com/ischoolsu/docs/su_ischool_innovations_18-19}{\textit{iSchool Innovations}}, ``Going old-school for new knowledge with Harvard, Oxford opportunities''\\

\footnotesize{2019} & \href{https://web.archive.org/web/20240724175744/https://ischool.syr.edu/three-doctoral-grads-taking-diverse-career-pathways-2019/}{\textit{Syracuse University iSchool News}}, ``Three doctoral grads taking diverse career pathways''\\

\footnotesize{2019} & \href{https://dailyorange.com/2019/04/aapi-heritage-month-exhibit-remembers-su-campus-hate-crime-raises-awareness/}{\textit{The Daily Orange}}, ``AAPI Heritage Month exhibit remembers SU campus hate crime, raises awareness''\\

\footnotesize{2019} & \href{https://www.i3-inclusion.org/news/i3-makes-a-strong-showing-at-iconference-2019/}{\textit{i3 News}}, ``i3 makes a strong showing at iConference 2019''\\

\footnotesize{2019} & \href{https://web.archive.org/web/20190329111213/https://ischool.syr.edu/articles/news/view/faculty-students-presenting-at-iconference-2019/}{\textit{Syracuse University iSchool News}}, ``Faculty, students presenting at iConference 2019''\\

\footnotesize{2018} & \href{https://web.archive.org/web/20190324053041/https://issuu.com/alist_magazine/docs/alist_summer_2018_final}{\textit{ALIST Magazine}}, ``The intersection of technology, innovation and human values with Bryan Dosono''\\

\footnotesize{2018} & \href{https://dailyorange.com/2018/04/asian-american-pacific-islander-students-celebrate-place-syracuse-university/}{\textit{The Daily Orange}}, ``Asian American and Pacific Islander students celebrate their place at Syracuse University''\\

\footnotesize{2018} & \href{https://web.archive.org/web/20240222194658/https://ischool.syr.edu/faculty-students-presenting-iconference-2018/}{\textit{Syracuse University iSchool News}}, ``Faculty, students presenting at iConference 2018''\\

\footnotesize{2018} & \href{https://cdn.coverstand.com/35468/480339/07e4eb31edcfe2fac898ccb79316b89262b1bbe7.pdf}{\textit{Mortar Board Forum}}, ``Scholarship matters''\\

\footnotesize{2017} & \href{https://web.archive.org/web/20200506203625/https://issuu.com/ischoolsu/docs/su_ischool_innovations_fall-18/47}{\textit{iSchool Innovations}}, ``Doctoral student recognitions, papers and presentations''\\

\footnotesize{2017} & \href{https://web.archive.org/web/20170822004200/https://ischool.syr.edu/articles/news/view/dosono-to-attend-acm-turing-award-celebration/}{\textit{Syracuse University iSchool News}}, ``Dosono to attend ACM's Turing Award Celebration''\\

\footnotesize{2017} & \href{https://web.archive.org/web/20190329111412/https://ischool.syr.edu/articles/news/view/faculty-staff-phd-students-presenting-iconference-2017/}{\textit{Syracuse University iSchool News}}, ``Faculty, staff, doctoral students presenting at iConference 2017''\\

\footnotesize{2016} & \href{https://surface.syr.edu/cgi/viewcontent.cgi?article=1020&context=ischool_newsletter}{\textit{Connections Magazine}}, ``iSchool researchers use technology to understand veteran reacclimation''\\

\footnotesize{2016} & \href{https://web.archive.org/web/20190329112000/https://ischool.syr.edu/articles/news/view/faculty-phd-students-presenting-at-iconference-2016/}{\textit{Syracuse University iSchool News}}, ``Faculty, doctoral students presenting at iConference''\\

\footnotesize{2015} & \href{https://web.archive.org/web/20240817024426/https://ischool.syr.edu/research-in-privacy-security-profiled-at-soups-conference/}{\textit{Syracuse University iSchool News}}, ``Research in privacy, security being profiled at SOUPS Conference''\\

\footnotesize{2014} & \href{https://dailyorange.com/2014/11/ischool-research-aims-to-aid-military-veterans-refugees/}{\textit{The Daily Orange}}, ``iSchool research aims to aid military veterans, refugees''\\

\footnotesize{2014} & \href{https://web.archive.org/web/20190329112131/https://ischool.syr.edu/articles/news/view/faculty-doctoral-students-presenting-at-iconference/}{\textit{Syracuse University iSchool News}}, ``Faculty, doctoral students presenting at iConference''\\

\footnotesize{2014} & \href{https://issuu.com/uwalumni/docs/viewpoint_2014fall}{\textit{Viewpoint}}, ``The husky experience''\\

\footnotesize{2014} & \href{https://web.archive.org/web/2026/https://news.syr.edu/blog/2014/10/28/students-park-bar-offers-workspace-seating-with-a-view-16177/}{\textit{Syracuse University iSchool News}}, ``Students' park bar offers workspace seating with a view''\\

\footnotesize{2013} & \href{https://dailyorange.com/2013/10/su-app-challenge-offers-1000-grand-prize/}{\textit{The Daily Orange}}, ``SU app challenge offers \$1,000 grand prize''\\

\footnotesize{2013} & \href{https://www.nwasianweekly.com/2013/07/uw-2013-eop-celebration-honors-3-apa-students/}{\textit{Northwest Asian Weekly}}, ``EOP celebration honors 3 APA students''\\

\footnotesize{2013} & \href{https://nwasianweekly.com/2013/05/what-should-we-celebrate-community-members-reflect-on-what-theyre-proud-of-during-apa-heritage-month/}{\textit{Northwest Asian Weekly}}, ``What should we celebrate? — Community members reflect on what they’re proud of during APA Heritage Month''\\

\footnotesize{2013} & \href{https://www.yakimaherald.com/news/local/wapato-resident-receives-uw-honor/article_c7041e94-ace9-5168-a364-d0b9206a6a41.html}{\textit{Yakima Herald Independent}}, ``Wapato resident receives UW honor''\\

\footnotesize{2013} & \href{https://www.dailyuw.com/news/article_e5e0683f-d959-5ce1-b1f2-4d23e797b379.html}{\textit{UW Daily}}, ``ECC honors community members for activism efforts''\\

\footnotesize{2012} & \href{https://www.dailyuw.com/news/article_3c781595-0b4d-52be-9a6e-b2c956ae72eb.html}{{UW Daily}}, ``Greek community participates in annual Greek Week''\\

\footnotesize{2012} & \href{https://www.washington.edu/alumni/columns/pdf/columns_september_2012.pdf}{\textit{Columns}}, ``Out and about''\\

\footnotesize{2012} & \href{https://issuu.com/uwalumni/docs/columns_201212}{\textit{Columns}}, ``Crowning glory''\\

%dosono moderator
\footnotesize{2011} & \href{https://www.dailyuw.com/features/article_17600702-c4b3-57ad-ac29-29a601b88da7.html}{\textit{UW Daily}}, ``Building Greek communities''\\
\end{longtable}}
\end{document}